### 2021-09-07 proposal-documents/doe/benefit-of-collaboration/benefit-of-collaboration.tex
added float package

%@TheDoctorRAB
%standard white paper/preproposal format
%
%%%%%
%
%REFERENCES
%
%neup.bst - numbered citations in order of appearance, short author list with et al in reference section
%nsf.bst - numbered citations in order of appearance, full author list in references section
%standard.bst - citations with author last name with et al for more than 2 authors; full author list in references section
%ans.bst is for ANS only. 
%
%author = {Lastname, Firstname and Lastname, Firstname and Lastname, Firstname} for all bst formats
%bst renders the author list itself
%
%author = {{Nuclear Regulatory Commission}} if the author is an organization, institution, etc., and not people
%
%title = {{}} for all
%
%for all - use \citep{-} - [1] or (Borrelli, 2021) in the text
%standard.bst \cite{-} - Borrelli (2021) in the text
%standard.bst lists references alphabetically
%the rest list numerically
%
%%%%%
\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage[pagewise]{lineno} %line numbering
\usepackage{setspace}
\usepackage{ulem} %strikethrough - do not \sout{\cite{}}
\usepackage[pdftex,dvipsnames]{xcolor,colortbl} %change font color
\usepackage{graphicx}
\usepackage{filecontents}
\usepackage{tablefootnote}
\usepackage{footnotehyper}
%\usepackage{subfig}
\usepackage[yyyymmdd]{datetime} %date format
\renewcommand{\dateseparator}{.}
\graphicspath{{../img/}} %path to graphics
\setcounter{secnumdepth}{5} %set subsection to nth level

@@

\subsection*{Summary of the Proposed Project}

\subsection*{Motivation} 
\paragraph*{Context.}

\paragraph*{Challenges to nuclear materials accounting.}

\subsection*{Overall Objective}

\subsection*{Research Focus} 
\noindent Project workscopes are summarized. 
\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item\textit{Title (Lead - )}
        \begin{itemize}[topsep=-1ex,itemsep=-1ex,partopsep=1ex,parsep=1ex]
            \item 
            \item 
        \end{itemize}
    \item\textit{}
        \begin{itemize}[topsep=-1ex,itemsep=-1ex,partopsep=1ex,parsep=1ex]
            \item 
            \item 
        \end{itemize}
    \item\textit{}
        \begin{itemize}[topsep=-1ex,itemsep=-1ex,partopsep=1ex,parsep=1ex]
            \item 
            \item  
        \end{itemize}
    \item\textit{Conclusions - Crosscutting issues (Full team)}
        \begin{itemize}[topsep=-1ex,itemsep=-1ex,partopsep=1ex,parsep=1ex]
            \item Identify lessons learned.
            \item Develop future research pathways.
        \end{itemize}
\end{enumerate}

\subsection*{Team} This research will facilitate collaboration among current industry experts with extensive \textit{fill in phrase about team expertise.} The project team consists of the following members. The contribution of each is noted. The corresponding facilities are briefly described thereafter.

@@

\subsection*{Important Research Facility/Equipment}
\noindent The Important Research Facility/Equipment is \textit{description as relevant to project.}

\subsection*{Work Project Documentation, Quality Control} 
\noindent The PI has a practiced a QA approach, consistent with that established by the DOE Technical Integration Office, per NEUP website and any additional requirements deemed necessary during contracting. All projects undergo safety review by experts. We have followed this QA expectation in all ongoing awards. We abide by current and pending information on nuclear-related federal funding contained in Form 3204. The Mandatory, Go/No-go, requirements will be coordinated with The University of Idaho Office of Sponsored Research, the general counsel and Technology Transfer. The PI assumes responsibility as the POC and follow these requirements: 1) Commitment to reporting and budget requirements, 2) 10CFR851 Worker Safety and Health Program, 3) Export Control and 4) Quality Assurance.

>>>>

%@TheDoctorRAB
%standard white paper/preproposal format
%
%%%%%
%
%REFERENCES
%
%neup.bst - numbered citations in order of appearance, short author list with et al in reference section
%nsf.bst - numbered citations in order of appearance, full author list in references section
%standard.bst - citations with author last name with et al for more than 2 authors; full author list in references section
%ans.bst is for ANS only. 
%
%author = {Lastname, Firstname and Lastname, Firstname and Lastname, Firstname} for all bst formats
%bst renders the author list itself
%
%author = {{Nuclear Regulatory Commission}} if the author is an organization, institution, etc., and not people
%
%title = {{}} for all
%
%for all - use \citep{-} - [1] or (Borrelli, 2021) in the text
%standard.bst \cite{-} - Borrelli (2021) in the text
%standard.bst lists references alphabetically
%the rest list numerically
%
%%%%%
\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage[pagewise]{lineno} %line numbering
\usepackage{setspace}
\usepackage{ulem} %strikethrough - do not \sout{\cite{}}
\usepackage[pdftex,dvipsnames]{xcolor,colortbl} %change font color
\usepackage{graphicx}
\usepackage{filecontents}
\usepackage{tablefootnote}
\usepackage{footnotehyper}
\usepackage{float}
%\usepackage{subfig}
\usepackage[yyyymmdd]{datetime} %date format
\renewcommand{\dateseparator}{.}
\graphicspath{{../img/}} %path to graphics
\setcounter{secnumdepth}{5} %set subsection to nth level

@@

\subsection*{Summary of the Proposed Project.}

\subsection*{Motivation.} 
%\paragraph*{Context.}

\subsection*{Overall Objective.}

\subsection*{Research Focus.} 
\noindent Project workscopes are summarized. 
\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item\textit{Title (Lead - )}
        \begin{itemize}[topsep=-1ex,itemsep=-1ex,partopsep=1ex,parsep=1ex]
            \item 
            \item 
        \end{itemize}
    \item\textit{}
        \begin{itemize}[topsep=-1ex,itemsep=-1ex,partopsep=1ex,parsep=1ex]
            \item 
            \item 
        \end{itemize}
    \item\textit{}
        \begin{itemize}[topsep=-1ex,itemsep=-1ex,partopsep=1ex,parsep=1ex]
            \item 
            \item  
        \end{itemize}
    \item\textit{Conclusions - Crosscutting issues (Full team)}
        \begin{itemize}[topsep=-1ex,itemsep=-1ex,partopsep=1ex,parsep=1ex]
            \item Identify lessons learned.
            \item Develop future research pathways.
        \end{itemize}
\end{enumerate}

\subsection*{Team.} 
This research will facilitate collaboration among current industry experts with extensive \textit{fill in phrase about team expertise.} The project team consists of the following members. The contribution of each is noted. The corresponding facilities are briefly described thereafter.

@@

\subsection*{Important Research Facility/Equipment.}
\noindent The Important Research Facility/Equipment is \textit{description as relevant to project.}

\subsection*{Work Project Documentation, Quality Control.} 
\noindent The PI has a practiced a QA approach, consistent with that established by the DOE Technical Integration Office, per NEUP website and any additional requirements deemed necessary during contracting. All projects undergo safety review by experts. We have followed this QA expectation in all ongoing awards. We abide by current and pending information on nuclear-related federal funding contained in Form 3204. The Mandatory, Go/No-go, requirements will be coordinated with The University of Idaho Office of Sponsored Research, the general counsel and Technology Transfer. The PI assumes responsibility as the POC and follow these requirements: 1) Commitment to reporting and budget requirements, 2) 10CFR851 Worker Safety and Health Program, 3) Export Control and 4) Quality Assurance.
